Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-11 paper.tex
Rewrite the intros in section 2.

Experience with our previous educational software
system has shown gratifying uptake and
use by children.  But we are often disappointed that some of our
favorite pedagogical tools included in the systems were not being
widely used.  Enthusiastic teachers would spark intensive use in
certain classrooms, but children had difficulty finding their way into
the material without strong guidance.

Children (like all humans) are hard-wired for
stories~\cite{boyd:stories}.  Nell uses a
\textit{Narrative Interface}~\cite{bizzocchi:narrative,don:narrative}
to guide the child user through the pedagogical capabilities of the
system.  All system actions are shaped by the storybook metaphor, and
interactions with the system are conceptualized as interactions with
one of the system protagonists.

@@

As illustrated in figure~\ref{fig:nell}, Nell's characters are
always-available agents layered above a particular system \textit{activity}
(application) which provides specialized functionality.  The agents
are not always foregrounded: constructionist learning occurs when the
child plays freely to ``make things'' with the base activity.
The handwriting tutor is fundamentally a drawing activity; the
adventure involving the magical musical lock is also a music-making activity.
%  ``Making things'' is the key to constructionist learning.
The narrative system is
hooked into each activity to provide passive guidance
(congratulating the child when it notices they've drawn a letter),
active guidance (Apple-Guide--style~\cite{powers:appleguide}
contextual help), or system services (switch activities; jump into a
related story module/lesson plan).

@@

The Nell system aims to have a ``low floor and no ceiling.''  The low
floor is a very simple base system, usable with no literacy skills or
external guidance.  The system then grows with the child's expanding
capabilities, serially accumulating story modules to tackle topics of
increasing difficulty.  As mentioned before, the ability for third
parties to independently author story modules is necessary to ensure
Nell can continue to grow.  There should be no external dependencies
limiting a child's ability to participate in this process: a Nell
system contains a story editor and everything necessary to
author and publish story modules.

@@

The constructionist learning philosophy emphasizes creation and
tangible interaction.  Nell uses direct interaction on a tablet
computer to maintain the child's connection to their work
(Fig.~\ref{fig:xo3}).

>>>>

Children (like all humans) are hard-wired for
stories~\cite{boyd:stories}, yet our prior Sugar Learning Platform
made no use of this fact. By contrast, Nell augments Sugar's
affordances for \textit{action}, \textit{reflection}, and
\textit{communication} with new affordances for \textit{engagement} organized
as a modular \textit{Narrative Interface}~\cite{bizzocchi:narrative,don:narrative}.
In this interface, all system actions are shaped by the storybook metaphor, and
interactions with the system are conceptualized as interactions with one of the
system protagonists.

@@

As depicted in Figure~\ref{fig:nell}, Nell's characters are
always-available agents layered above a particular system \textit{activity}
(application) which provides specialized functionality.  The agents
are not always foregrounded: constructionist learning occurs when the
child plays freely to ``make things'' with the base activity.
The handwriting tutor is fundamentally a drawing activity; the
adventure involving the magical musical lock is also a music-making activity.
%  ``Making things'' is the key to constructionist learning.
The narrative system is
hooked into each activity to provide passive guidance
(congratulating the child when it notices they've drawn a letter),
active guidance (Apple-Guide--style~\cite{powers:appleguide}
contextual help), or system services (switch activities; jump into a
related story module/lesson plan).

@@

Children grow. To accommodate them, Nell provides a ``low floor and
no ceiling.''  The low
floor is a very simple base system, usable with no literacy skills or
external guidance.  The system then grows with the child's expanding
capabilities, serially exposing story modules to tackle topics of
increasing difficulty.  Later, the ability for third
parties to independently author story modules ensures that
Nell can continue to grow.  Finally, there are no external dependencies
limiting a child's ability to participate in this process: a Nell
system contains a story editor and everything necessary to
author and publish story modules.

@@

Children construct knowledge from direct interactive
experience~\cite{Papert91}. As a result, (and like its predecessor Sugar), Nell
emphasizes creation and tangible interaction by using direct interaction; this
time, using a tablet computer to maintain the child's connection to their work
(Fig.~\ref{fig:xo3}).
